Rigidity of Expectations: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-07-10 paper/Draft.tex
rewrote the data section on SCE including 1-year and 2-year ahead

	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probabilistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

@@

	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including headline CPI and PCE inflation they have started eliciting since 2007. In particular, the density forecasts are both made for current year forecast, basically nowcasting, as well as one-year-ahead forecast. This allows for directly testing the implications from the revisions in uncertainty.

	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 has at least met the first criteria. In particular, households are asked to provide their perceived probabilities to 1-year-ahead inflation for a range of values. \footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one. NY Fed stuff has excluded those who do not meet this criteria.} The high-frequency monthly panel structure also provides an invaluable chance to explore the dynamics of uncertainty. Around one third of the households are surveyed for 12 months.

@@

	\section{Shock-based tests of expectation rigidity }\label{ShockBased}

@@

	(1) Technology shock is identified from a three variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts. Based on Bayes information criterion, I use the lag of 4 quarters as in \citet{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share approach'' developed by \citet{francis2014flexible}. It is shown to have better small-sample properties. In particular,  the approach defines technology shock as the variation of current period labor productivity (output per hour) that explains the maximum fraction of future labor productivity over an exogenously determined horizon. The results using this shock will be included in a later version of the paper. For the replication purpose now, I stay with \citet{gali1999technology}}. The sample period used to identify the shock is 1949-2019, while the period where it enters my analysis is the same to the period of survey data: 2007-2019 for SPF and 2013-2019 for SCE.

>>>>

	Third, \citet{manski2004measuring} and many other papers have advocated long for eliciting probabilistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{bertrand2001people} and other work have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond the revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

@@

	Survey of Professional Forecasters(SPF) meet both criteria thanks to the density forecasts of a number of macroeconomic variables, including core CPI and core PCE inflation they have started eliciting since 2007, as well as a longer series of GDP deflator dating back to 1968. This paper focus on the first two, for which both forecast for current-year inflation, basically nowcast, and one-year-ahead forecast are based on densities. This make it possible to directly test the implications about the revisions in uncertainty across different vintages of forecasts.

	The New York Fed Survey of Consumer Expectation(SCE) that started in 2013 meet the first criteria and half of the second. In particular, households are asked to provide their perceived probabilities about 1-year-ahead and 2-year-ahead inflation for various ranges of values\footnote{Most importantly, they are kindly reminded that all the probabilities need to add up to one. NY Fed stuff has excluded those who do not meet this criteria.}. This allows for comparing 2-year-ahead forecast at time $t-2$ with 1-year-ahead forecast at $t-1$. Since the maximum duration for households to stay in the panel is 12 months (for about one third of the households),  forecast revision can be only examined in the population level. The advantage of SCE compared to SPF is its monthly frequency. This provides an invaluable chance to explore the dynamics of uncertainty.

@@

	\section{Shock-based Estimates of Expectation Rigidity }\label{ShockBased}

@@

	(1) Technology shock is identified from a three-variate structural vector autoregression(SVAR) model  (output per capita, hours and inflation) by imposing a widely used long-run restriction that non-technology shocks have no long-run output impacts. Based on Bayes information criterion, I use the lag of 4 quarters as in \citet{coibion2012can} \footnote{A recent alternative to long-run restriction approach is the ``max-share approach'' developed by \citet{francis2014flexible}. It is shown to have better small-sample properties. In particular,  the approach defines technology shock as the variation of current period labor productivity (output per hour) that explains the maximum fraction of future labor productivity over an exogenously determined horizon. The results using this shock will be included in a later version of the paper. For the replication purpose now, I stay with \citet{gali1999technology}}. The sample period used to identify the shock is 1949-2019, while the period where it enters my analysis is the same to the period of survey data: 2007-2019 for SPF and 2013-2019 for SCE.
